citecorp
=========

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Build Status](https://travis-ci.com/ropenscilabs/citecorp.svg?branch=master)](https://travis-ci.com/ropenscilabs/citecorp)

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

Client for the Open Citations Corpus

## Install

Development version

```{r eval=FALSE}
devtools::install_github("ropenscilabs/citecorp")
```

```{r}
library("citecorp")
```

## Open citations methods

```{r}
oc_doi2ids("10.1097/igc.0000000000000609")
oc_pmid2ids("26645990")
oc_pmcid2ids("PMC4679344")
```

## Meta

* Please [report any issues or bugs](https://github.com/ropenscilabs/citecorp/issues)
* License: MIT
* Get citation information for `citecorp` in R doing `citation(package = 'citecorp')`
* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
